```{r}
library(wordcloud);
library(tm);

require(RColorBrewer);
```
There are two datasets: esplanade and sistic. Each contains 3 categories:dance, music, theatre.

Read esplanade dataset 
```{r}
esp.dance   = read.delim('data/data.dance.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
esp.music   = read.delim('data/data.music.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
esp.theatre = read.delim('data/data.theatre.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
```
Read sistic dataset 
```{r}
sis.dance   = read.delim('data/sistic.dance.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
sis.music   = read.delim('data/sistic.music.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
sis.theatre = read.delim('data/sistic.theatre.tsv', header = T, sep = '\t', stringsAsFactors = FALSE, quote = "")
```

Categorize data by groups and merge
```{r}
dance   = rbind(esp.dance, sis.dance); dance$id = 1
music   = rbind(esp.music, sis.music); music$id = 2
theatre = rbind(esp.theatre, sis.theatre); theatre$id = 3
data = rbind(dance, music, theatre)
nrow(data)
```

Extracting, preprocessing,encoding text from data and procuding document-term-matrix 
```{r}
Corp = Corpus(VectorSource(data[,2]))
Corp = tm_map(Corp, PlainTextDocument)
Corp = tm_map(Corp, content_transformer(tolower))
Corp = tm_map(Corp, removePunctuation)
Corp = tm_map(Corp, removeWords, c(stopwords("english")))
dtm  = DocumentTermMatrix(Corp)
dtm  = removeSparseTerms(dtm, 0.90)
DTM = as.data.frame(as.matrix(dtm))

DTM_freq = colSums(DTM)
thr_100 = sort(DTM_freq, decreasing = TRUE)[5]
DTM = DTM[ , DTM_freq < thr_100]
data$DESCRIPTION = NULL
data = cbind(data, DTM)
```

Draw word cloud
```{r}
dtm_dan = data[data$id == 1, -c(1:6)]
dtm_mus = data[data$id == 2, -c(1:6)]
dtm_the = data[data$id == 3, -c(1:6)]
```
Drawing wordclouds for each cat
```{r}
pal2 <- brewer.pal(8,"Dark2")
wordcloud(colnames(dtm_dan), colSums(dtm_dan),scale = c(2,0.5),min.freq = 10, colors=pal2)
wordcloud(colnames(dtm_mus), colSums(dtm_mus),scale = c(2,0.5),min.freq = 30, colors=pal2)
wordcloud(colnames(dtm_the), colSums(dtm_the),scale = c(2,0.5),min.freq = 10, colors=pal2)
```

Logistic Regression with raw frequency
Logistic Regression for cat dance
```{r}
label_dtm = data[, - c(1:5)]
label_dtm$id = as.numeric(label_dtm$id == 1)
label_dtm$id = as.factor(label_dtm$id)
lg_1 = glm(formula = id ~ . , family = "binomial", data = label_dtm)
summary(lg_1)
```
Logistic Regression for cat music
```{r}
label_dtm = data[, - c(1:5)]
label_dtm$id = as.numeric(label_dtm$id == 2)
label_dtm$id = as.factor(label_dtm$id)
lg_2 = glm(formula = id ~ . , family = "binomial", data = label_dtm)
summary(lg_2)
```
Logistic Regression for cat theatre
```{r}
label_dtm = data[, - c(1:5)]
label_dtm$id = as.numeric(label_dtm$id == 3)
label_dtm$id = as.factor(label_dtm$id)
lg_3 = glm(formula = id ~ . , family = "binomial", data = label_dtm)
summary(lg_3)
```





